\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-11 TPDP2018/poster/main.tex
some work

\author{Mark Bun$^\dag$,
%Imdea Software\\[-3mm]
%\texttt{gjbarthe@gmail.com} \\
%\And 
Gian Pietro Farina$^{*}$,
%University of Dundee\\[-3mm] 
%\texttt{g.p.farina@dundee.ac.uk} \\
%\And
Marco Gaboardi$^{*}$,
%University of Dundee\\[-3mm] 
%\texttt{m.gaboardi@dundee.ac.uk} \\
%\And
Jiawen Liu$^{*}$
%Imdea Software
%\texttt{pierre-yves@strub.nu} \\
}

\institute{$^\dag$Princeton University, $^{*}$University at Buffalo, SUNY} % Institution(s)

@@

\begin{block}{Objectives}
% \begin{columns} % Subdivide the first main column
% \begin{column}{.69\textwidth}
\begin{enumerate}
\item Designing a differentially private Bayesian inference mechanism.
\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$), $f$-divergence, etc.).
% \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
% \item Applying smooth sensitivity in mechanism to achieve better accuracy.
%         (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
\end{enumerate}
% \end{column}
% \begin{column}{.28\textwidth}
% \begin{figure}[ht]
% \centering
% \includegraphics[width=0.85\textwidth]{poster_0.eps}
% say something about beta...
% \caption{\footnotesize{Local sensitivity of Hellinger}}
% \label{fig_sensitivity}
% \end{figure}
% \vspace{.1cm}
% \end{column}
% \end{columns}

% \noindent Design a mechanism that achieve differential privacy by scaling to a metric between distribution.
% \begin{enumerate}
% \item A differentially private bayesian mechanism,
% \item Calibrating mechanism noise by the same probabilistic distance we want to measure accuracy with.
% \item Applying smooth sensitivity in mechanism to achieve better accuracy.
% \end{enumerate}

@@

\begin{block}{Bayesian inference ($\bysinfer$) (A Beta-Binomial model example):}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
%The prior $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$ is conjugate to the likelihood function.
\begin{itemize}
  \item[-] Prior on $\theta: \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data set $\dataobs= (x_1,\dots x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.

  \item[-] Likelihood function: $\mathbb{L}_{\dataobs | \theta}= \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$;

  \item[-] Posterior distribution over theta: $\mathbb{P}_{\theta|\dataobs}=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$.
\end{itemize}
\end{block}
% and with p.d.f:

@@

\begin{block}{Differentially Private Bayesian Inference and Motivations}
Releasing a differentially private posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}
  \item  Baseline approach is Laplace mechanism (LapMech) with sensitivity proportional to $\ell_1$ norm. But this sensitivity grows linear with the dimension, also we measure results by a different metric. Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$). %(v.s. the $\ell_1$ norm in baseline approach).} \todo{} % \todo{give formula of hellinger Distance, give the Dirichlet distribution, no need to formal expression, Laplace with mean and scale in 2 dimension.}
  \item Maximum sensitivity of $\hellinger$ over $\betad$ distributions achieves at edges as in Fig. \ref{fig_sensitivity}. But it's very low when move away from edge. Motivated by this, we apply smooth sensitivity in mechanism to improve accuracy.
  %{sensitivity is maximize when plot of hellinger distance of alpha and beta variance between adjacent data bases, of varying }
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivities of $\hellinger$ over $\betad$}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

\begin{block}{Smoothed Hellinger Distance Based Exponential Mechanism}

We define the mechanism $\hexpmech$ which produces an element $r$ in $\betaset$ with probaiblity:
\[
% \underset{z \thicksim \hexpmech}{\Pr}[z=r] = 
\mathbb{P}_{r \thicksim \hexpmech} =
\frac 
{\exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
{\sum_{r\in\betaset} \exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
\]

given in input an observations $\dataobs$, parameters $\epsilon>0$ and $\delta>0$, where:

\begin{itemize}
  \item[-] $\betaset$, the candidates set defined as $\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$, given the prior distribution $\bprior=\betad(\alpha, \beta)$ and observed data set size $n$.

  \item[-] $-\hellinger(\bysinfer(\dataobs),r)$ denotes the scoring function based on the Hellinger distance.

  \item[-] $S(\dataobs)$, the smooth sensitivity\cite{nissim2007smooth}:
  $
  S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\big\{ LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\big\}
  $,
  where:
  \begin{itemize}
   \item $d$: Hamming distance between two data sets,

   \item $LS(\dataobs')$, local sensitivity at $\dataobs'$:
   $
   LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert
   $,

   \item $\gamma =   \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$ to ensure the $(\epsilon,\delta)$-differentially private.
 \end{itemize}
\end{itemize}

@@

\begin{block}{Preliminary Experimental Results}
% Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
Experiments are on three mechanisms and plotted as follows:
\begin{itemize}
  \item[-] \textbf{Green}: Baseline approach. (noises being postprocessed to floor value) %adds noise scaled to sensitivity proportional to dimensionality,
  \item[-] \textbf{Red}: LapMech with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
  (posteriors of adjacent data sets differ only in two dimensions).
  \item[-] \textbf{Blue}: $\hexpmech$.
\end{itemize}
  Fig. \ref{fig_sampling} and Fig. \ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size or prior configuration.

\begin{figure}[H]
\begin{center}
\centering
  \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
    \includegraphics[width=0.333\textwidth]{poster_1.eps}
    \label{subfig_sampling_2d}
  }
  \subfigure[\footnotesize{3 dimensions, data size $\in [100,500]$} ]{
    \includegraphics[width=0.302\textwidth]{poster_2.eps}
  \label{subfig_sampling_3d}
  } 
  \subfigure[\footnotesize{4 dimensions, data size $\in [100,600]$}]{
    \includegraphics[width=0.295\textwidth]{poster_3.eps}
    \label{subfig_sampling_4d}
  }
  \caption{Average accuracy by increasing data set size}
\label{fig_sampling}
\end{center}
\end{figure}

Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} give us the discrete probabilities. On the x-axis: the distance of a potential output r from the true answer and on y-axis the probability of r being output by the mechanisms.
\begin{figure}[H]
\begin{center}
\centering
   \subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.313\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\caption{4-quantile and discrete probability plots}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$ (except Fig. \ref{subfig_prior}) , balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}

>>>>

\author{Mark Bun$^\dag$,
Gian Pietro Farina$^{*}$,
Marco Gaboardi$^{*}$,
Jiawen Liu$^{*}$
}

\institute{$^{\dag}$Princeton University, $^{*}$University at Buffalo, SUNY} % Institution(s)

@@

\begin{block}{Objectives}
% \begin{columns} % Subdivide the first main column
% \begin{column}{.69\textwidth}
\begin{enumerate}
\item Design a differentially private Bayesian inference mechanism.
\item Improve accuracy by calibrating noise  to the sensitivity of a
         metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots).
\end{enumerate}
\end{block}

@@

\begin{block}{Bayesian inference ($\bysinfer$), the Beta-Binomial model example:}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
%The prior $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$ is conjugate to the likelihood function.
\begin{itemize}
  \item  Prior on {\small $\theta: \mathbb{P}_{\theta}= \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data $\dataobs= (x_1,\dots, x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.}

  \item  Likelihood function: {\small $\mathbb{L}_{\theta|\dataobs }= \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}$, where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}x_i$.}

  \item Posterior on {\small $\theta$: $\bysinfer(x)\equiv\mathbb{P}_{\theta|\dataobs}=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)\propto\mathbb{L}_{\theta|\dataobs }\cdot \mathbb{P}_{\theta}$.}
\end{itemize}
\end{block}
% and with p.d.f:

@@

\begin{block}{Differentially private Bayesian inference and motivations}
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}
\item  Baseline approach: 
  \begin{itemize}
  \item Release $\betad(\alpha +  \lfloor\widetilde{\Delta \alpha}\rfloor^n_0,\beta + n - \lfloor\widetilde{\Delta \alpha}\rfloor^n_0)$,
  \item $\widetilde{\Delta \alpha}\sim \lap{\Delta\alpha}{\frac{S}{\epsilon}}$
  \item \todo{$S\propto ||\cdot ||_{1}$}.
  \item Measure accuracy with a metric over distributions, e.g. $\hellinger$.
  \end{itemize}
  {\color{red}{But $S$ grows linearly with the dimension: too noisy when we generalize to Dirichlet-Multinomial ({\small$\dirichlet(\cdot)$}) model}}. 
\item Another approach:
  \begin{itemize}
    \item Calibrate  noise w.r.t \emph{global} sensitivity of $\hellinger$: {\color{red}{but global sensitivity is still too big.}}
    \item Fig. \ref{fig_sensitivity} shows that there is a gap between global and local sensitivity of $\hellinger$.
    \end{itemize}
  \item A better approach:
    \begin{itemize}
      \item \large{Calibrate noise w.r.t. the \emph{smooth} sensitivity of $\hellinger$.}
    \end{itemize}
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivity of $\hellinger$. There is a gap between Global and Local sensitivity.}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

\begin{block}{Our approach: smoothed Hellinger distance based exponential mechanism}

We define the mechanism $\hexpmech$ which produces an element $r$ in $\betaset$ with probability:
\[
\mathbb{P}_{r \thicksim \hexpmech} =
\frac 
{\exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
{\sum_{r\in\betaset} \exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
\]
where:
\begin{itemize}
 \small{ \item  $\betaset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\}$. With prior distribution $\bprior=\betad(\alpha, \beta)$.}
  \item \small{$-\hellinger(\bysinfer(\dataobs),r)$ denotes the scoring function.}

  \item \small{$S(\dataobs)\equiv \max_{\dataobs' \in \{0,1\}^{n}}\big\{ LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\big\}$: smooth sensitivity\cite{nissim2007smooth}}, $d$ is the
    Hamming distance.
   \item \small{$LS(\dataobs')\equiv\max\limits_{y\in \datauni^n:\adj{y}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(y), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert$ is the local sensitivity of $\dataobs',\gamma =   \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$}.
 \end{itemize}

@@

  \begin{block}{Preliminary Experimental Results}
    Experiments are on three mechanisms and plotted as follows:
\begin{itemize}
  \item[-] {\textbf{\color{green}{Green}}}: Baseline approach. %adds noise scaled to sensitivity proportional to dimensionality,
  \item[-] {\textbf{\color{red}{Red}}}: Improved baseline approach with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
  (posteriors of adjacent data sets differ only in two dimensions).
  \item[-] {\textbf{\color{blue}{Blue}}}: $\hexpmech$.
\end{itemize}
% In Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the
% probability of the distributions with that distance under the different mechanisms. In Fig. \ref{subfig_prior} we present the influence of the prior on the accuracy of the three mechanisms,
% by showing the quartiles of the experimental distribution of the Hellinger distance.
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.313\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }

% \caption{4-quantile and discrete probability plots}
% \label{fig_concrete_prob}
% \end{center}
% \end{figure}
% % Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
%   Fig. \ref{fig_sampling} and Fig. \ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior.
% \begin{figure}[H]
% \begin{center}
% \centering
  \subfigure[\footnotesize{2 dimensions, data size $\in [100,500]$}]{
    \includegraphics[width=0.333\textwidth]{poster_1.eps}
    \label{subfig_sampling_2d}
  }
  \subfigure[\footnotesize{3 dimensions, data size $\in [100,500]$} ]{
    \includegraphics[width=0.302\textwidth]{poster_2.eps}
  \label{subfig_sampling_3d}
  } 
  \subfigure[\footnotesize{4 dimensions, data size $\in [100,600]$}]{
    \includegraphics[width=0.295\textwidth]{poster_3.eps}
    \label{subfig_sampling_4d}
  }
  \caption{Priors are $\betad(1,1), \dirichlet(1,1,1)$ and $\dirichlet(1,1,1,1)$ (except for Figure \ref{subfig_prior}) ,
    balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$. }
\label{fig_sampling}
\end{center}

\end{figure}
